%------------------------
% Resume in Latex
% Author : Bhavya Singh
% License : MIT
%------------------------
\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
% Use lmodern for better compatibility than cfr-lm while maintaining the look
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Tight margins to fit on one page
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\usepackage[most]{tcolorbox}
\tcbset{ frame code={}, center title, left=0pt, right=0pt, top=0pt, bottom=0pt, colback=gray!20, colframe=white, width=\dimexpr\textwidth\relax, enlarge left by=-2mm, boxsep=4pt, arc=0pt,outer arc=0pt, }
\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large }{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]
%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{ \item{ \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}} } }
\newcommand{\resumePOR}[3]{ \vspace{0.5mm}\item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} \end{tabular*} \vspace{-2mm} }
\newcommand{\resumeSubheading}[4]{ \vspace{0.5mm}\item \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1} & \textit{\footnotesize{#4}} \\ \textit{\footnotesize{#3}} & \footnotesize{#2}\\ \end{tabular*} \vspace{-2.4mm} }
\newcommand{\resumeProject}[4]{ \vspace{0.5mm}\item \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1} & \textit{\footnotesize{#3}} \\ \footnotesize{\textit{#2}} & \footnotesize{#4} \end{tabular*} \vspace{-2.4mm} }
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{\textbullet} % Solid bullet for outer lists
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{% \vspace{2mm}
\begin{tcolorbox}
\textbf{\large #1}
\end{tcolorbox}
\vspace{-4mm} }
% New command for hollow bullets
\newcommand{\resumeHollowItemListStart}{\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,label=\textopenbullet,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeHollowItemListEnd}{\end{itemize}\vspace{-2mm}}
\usepackage{amssymb}
% \newcommand{\textopenbullet}{$\circ$}
%---- Personal identifiers ----
\newcommand{\name}{Bhavya Singh}
\newcommand{\phone}{6377303089}
\newcommand{\emaila}{bhavyasingh27112004@gmail.com}
\newcommand{\linkedin}{linkedin.com/in/bhavyasinghiiitk}
\newcommand{\github}{github.com/waygeance}
\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------
\begin{center}
{\Huge \scshape \name} \\\vspace{2pt}
{\fontsize{9pt}{11pt}\selectfont \raisebox{-0.1\height}{\fontsize{9pt}{11pt}\selectfont \faPhone}\ +91-\phone ~|~ \raisebox{-0.1\height}{\fontsize{9pt}{11pt}\selectfont \faEnvelope}\ \href{mailto:\emaila}{\emaila} ~|~ \raisebox{-0.1\height}{\fontsize{9pt}{11pt}\selectfont \faLinkedin}\ \href{https://\linkedin}{\linkedin} ~|~ \raisebox{-0.1\height}{\fontsize{9pt}{11pt}\selectfont \faGithub}\ \href{https://\github}{\github}}
\end{center}
%-----------SUMMARY-----------
% START SUMMARY
\section{\textbf{Summary}}
\small{[Generated from Job Description at runtime]}
% END SUMMARY
%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading { B.Tech Electronics \& Communication Engineering}{CGPA: 7.1 / 10} {Indian Institute of Information Technology, Kota (IIIT-K)}{Graduated: 2027}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
\resumeSubheading { Software Development Engineer Intern | Frontend Focus}{Remote}{ DiCoTr AI}{August 2025 -- Present}
\vspace{+1.0mm}
\resumeHollowItemListStart
\item {Collaborated directly with the design team to translate high-fidelity Figma designs into a pixel-perfect Next.js and TypeScript web platform, ensuring 100\% design consistency.}
\item {Optimized the application for performance and SEO, achieving a 95+ Google Lighthouse score and improving organic search visibility by 25\%.}
\item {Participated in daily Agile Scrums and sprint planning, streamlining communication and improving the team's development velocity by 20\%.}
\item {Authored and maintained comprehensive technical documentation for the codebase, reducing onboarding time for new developers by 30\%.}
\resumeHollowItemListEnd
\resumeSubHeadingListEnd



%-----------PROJECTS-----------
% START PROJECTS
\section{\textbf{Projects}}
\resumeSubHeadingListStart

% ---------------- SDE / CORE ----------------
\resumeProject{Scalable REST API Service | Node.js, Express, MongoDB}{}{}{}
\resumeHollowItemListStart
\item {Designed RESTful APIs supporting high-concurrency access with optimized database schemas.}
\item {Reduced API latency by 40\% using indexing, caching, and query optimization.}
\item {Implemented structured logging and centralized error handling for maintainability.}
\resumeHollowItemListEnd

\resumeProject{Algorithmic Problem Solver | C++, STL, Competitive Programming}{}{}{}
\resumeHollowItemListStart
\item {Solved 500+ algorithmic problems across data structures, greedy, and dynamic programming.}
\item {Optimized solutions under strict time and memory constraints.}
\item {Improved problem-solving efficiency through contest-based practice.}
\resumeHollowItemListEnd

% ---------------- FRONTEND ----------------
\resumeProject{High-Performance Web Platform | Next.js, TypeScript}{}{}{}
\resumeHollowItemListStart
\item {Built modular frontend architecture with reusable components for scalability.}
\item {Used server-side rendering (SSR) to achieve 90+ Lighthouse performance and SEO scores.}
\item {Improved UX consistency and reduced runtime bugs via strict TypeScript typing.}
\resumeHollowItemListEnd

\resumeProject{Responsive Dashboard UI | React, Tailwind CSS}{}{}{}
\resumeHollowItemListStart
\item {Developed responsive dashboards optimized for mobile and desktop devices.}
\item {Improved render performance using memoization and efficient state management.}
\item {Ensured accessibility compliance with semantic HTML and ARIA standards.}
\resumeHollowItemListEnd

% ---------------- BACKEND ----------------
\resumeProject{Authentication \& Authorization System | JWT, RBAC}{}{}{}
\resumeHollowItemListStart
\item {Implemented secure login and role-based access control using JWT tokens.}
\item {Handled session expiry and token validation to prevent unauthorized access.}
\item {Designed middleware for reusable security enforcement across services.}
\resumeHollowItemListEnd

\resumeProject{Database Optimization Engine | MongoDB, Indexing}{}{}{}
\resumeHollowItemListStart
\item {Analyzed query patterns and implemented compound indexes.}
\item {Reduced average query execution time by 45\%.}
\item {Maintained data consistency under concurrent access.}
\resumeHollowItemListEnd

% ---------------- SDET / QA ----------------
\resumeProject{Automated Testing Framework | Jest, Cypress}{}{}{}
\resumeHollowItemListStart
\item {Developed unit, integration, and end-to-end test suites.}
\item {Reduced production bugs by 30\% through early detection.}
\item {Integrated tests into CI pipelines for continuous quality assurance.}
\resumeHollowItemListEnd

\resumeProject{API Testing Suite | Postman, Newman}{}{}{}
\resumeHollowItemListStart
\item {Designed comprehensive API test cases covering edge cases and failures.}
\item {Automated regression testing to ensure backward compatibility.}
\item {Improved API reliability while reducing manual testing effort.}
\resumeHollowItemListEnd

% ---------------- UI / UX ----------------
\resumeProject{User-Centered Redesign | Figma, UX Research}{}{}{}
\resumeHollowItemListStart
\item {Conducted usability studies to identify friction points in user workflows.}
\item {Redesigned user journeys, reducing task completion time by 25\%.}
\item {Created wireframes and high-fidelity prototypes aligned with accessibility standards.}
\resumeHollowItemListEnd

\resumeProject{Design System Development | UI Components}{}{}{}
\resumeHollowItemListStart
\item {Built reusable UI components to ensure design consistency across products.}
\item {Improved collaboration between designers and developers.}
\item {Reduced UI rework by standardizing typography, spacing, and color tokens.}
\resumeHollowItemListEnd

% ---------------- DATA / ANALYTICS ----------------
\resumeProject{Business Intelligence Dashboard | Power BI, SQL}{}{}{}
\resumeHollowItemListStart
\item {Developed interactive dashboards to track KPIs and business metrics.}
\item {Enabled data-driven decision-making with real-time insights.}
\item {Integrated multiple data sources for consolidated reporting.}
\resumeHollowItemListEnd

\resumeProject{Data Cleaning \& Analysis Pipeline | Python, Pandas}{}{}{}
\resumeHollowItemListStart
\item {Processed and cleaned large datasets to improve data accuracy.}
\item {Performed exploratory data analysis to identify trends and anomalies.}
\item {Generated stakeholder-ready reports using visual summaries.}
\resumeHollowItemListEnd

% ---------------- AI / SYSTEMS ----------------
\resumeProject{AI Resume Generator | LaTeX, Ollama LLMs}{}{}{}
\resumeHollowItemListStart
\item {Built an AI-powered system to generate structured LaTeX resumes automatically.}
\item {Integrated local LLM inference using Ollama for privacy-preserving generation.}
\item {Automated PDF generation using pdflatex with dynamic content injection.}
\resumeHollowItemListEnd

\resumeProject{System Automation Tooling | Linux, Bash}{}{}{}
\resumeHollowItemListStart
\item {Automated system maintenance tasks using shell scripts.}
\item {Improved developer productivity through CLI-based workflows.}
\item {Reduced manual intervention by scheduling recurring jobs.}
\resumeHollowItemListEnd

% ---------------- DEVOPS ----------------
\resumeProject{Containerized Development Environment | Docker}{}{}{}
\resumeHollowItemListStart
\item {Containerized services for consistent development and deployment environments.}
\item {Simplified onboarding by reducing environment setup complexity.}
\item {Managed service dependencies using Docker Compose.}
\resumeHollowItemListEnd

\resumeSubHeadingListEnd
% END PROJECTS




%-----------SKILLS-----------
% START SKILLS
\section{\textbf{Technical Skills}}
\begin{itemize}[leftmargin=0.05in, label={}]
\small{\item{ \textbf{Languages:} C, C++, JavaScript, TypeScript \\ \textbf{Web Technologies:} MERN Stack (MongoDB, Express.js, React, Node.js), Next.js, Tailwind CSS \\ \textbf{Cloud \& Tools:} Git, GitHub, Docker, VS Code, Sublime, Linux, AWS\\ \textbf{Core Concepts:} Algorithms, Data Structures, Operating Systems, OOP }}
\end{itemize}
% END SKILLS
%-----------AWARDS & CERTIFICATIONS-----------
\section{\textbf{Awards \& Certifications}}
\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=1mm]\small
\item \textbf{Meta Hacker Cup (2025):} Ranked 2020 out of 20,000+ candidates globally in round 2.
\item \textbf{Hacktoberfest Super Contributor:} Recognized as a top contributor for active open-source contributions.
\item \textbf{Finalist, IIT Jodhpur National Hackathon (2025):} Led a 6-member team to achieve a Top 7 position out of 200+ national teams.
\item \textbf{Finalist, Shaastra Programming Contest, IIT Madras (2025):} Finalist in one of India's most prestigious competitive programming contests.
\item \textbf{Ranked in Top 5\%, GenSolve Hackathon by Adobe (2024):} Recognized for excellence in machine learning-driven approaches.
\end{itemize}
\end{document}
